Stock enhancement undermines community stability

### 2022-02-18 rmd/manuscript.Rmd
edit: manuscript

Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999]. Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences. The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].

@@

We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios. These scenarios cover a range of ecological contexts, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Materials and Methods**). Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$). We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer underlying mechanisms.

@@

Competition is a likely mechanism, as our theory assumes. Field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015]. Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@weberInteractionsHatcheryWild2003]. Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities. As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.

@@

We cannot exclude the possibility that spurious correlations drove our results. However, the protected watersheds preserve nearly intact landscapes (average forest coverage: `r round(mean(df_env$frac_forest), 2) * 100`%; see **Figure S10**) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships. Further, we have statistically controlled natural variation in environmental factors (see **Materials and Methods** and **Tables S8-S10**). This unique setup may have helped uncover the close agreement between theory and empirical patterns.

Despite the significant attention to the fate of captive-bred individuals [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996], current schemes rarely consider the self-regulation process of biodiversity. Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning of ecosystem services [@cardinaleBiodiversityLossIts2012]. While our empirical example is limited to stream fish communities, we anticipate that this phenomenon is pervasive across terrestrial and aquatic taxa because the destabilizing effect emerged across diverse simulated scenarios.

>>>>

Here, we show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999]. Our theory illuminates that stock enhancement compromises the stabilizing mechanism emerging from species niche differences. The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].

@@

We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios. These scenarios cover a range of ecological contexts, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Materials and Methods**). Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: coefficient of variation (CV), number of species persist (defined as $N_i > 0.01$ at $t=1600$), temporal mean ($\mu$), and temporal SD ($\sigma$). We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer underlying mechanisms.

@@

Competition is a likely mechanism, as our theory assumes. Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@weberInteractionsHatcheryWild2003]. Indeed, field and experimental studies confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaWildMasuSalmon2018; @sahashiEvaluationContributionHatchery2015]. Importantly, socioeconomic factors control the number of releases (e.g., budget allocation) regardless of the current condition of recipient communities. As such, released fish are probably "excessive" and may cause resource competition that would otherwise not exist.

@@

We cannot exclude the possibility that spurious correlations drove our results. However, the protected watersheds preserve nearly intact landscapes (**Figure S10**) with strict regulations of human activities (e.g., exploitation, construction of in-stream structures); therefore, it is difficult to envision that unmeasured human influences caused the observed relationships. Further, we have statistically controlled natural variation in environmental factors (see **Materials and Methods** and **Tables S8-S10**). This unique setup may have helped uncover the qualitative agreement between theory and empirical patterns.

Despite the significant attention to the fate of captive-bred individuals [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996], current schemes rarely consider the self-regulation process of biodiversity. Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning of ecosystem services [@cardinaleBiodiversityLossIts2012]. While our empirical example is limited to stream fish communities, we anticipate that this phenomenon is pervasive in nature because the destabilizing effect emerged across diverse simulated scenarios.
